\begin{thebibliography}{99}

\bibitem{bail-stev}
  R. F. Bailey and B. Stevens,
  Hamiltonian decompositions of complete $k$-uniform hypergraphs.
  {\em Discrete Math}. 310 (2010), 3088-3095.

\bibitem{baran}
  Zs. Baranyai,
  On the factorization of the complete uniform hypergraph, Infinite and finite
  sets, Vol. I, pp.91-108.
  {\em Colloq. Math. Soc. Janos Bolyai}, 10 North-Holland, Amsterdam, 1975.

\bibitem{berge} 
  C. Berge,
  {\em Graphs and Hypergraphs}.
  7 North-Holland, Amsterdam, 1973.

\bibitem{bermond}
  J.C. Bermond,
  Hamiltonian decompositions of graphs, directed graphs and
  hypergraphs.
  {\em Ann. Discrete Math.} 3 (1978), 21-28.

\bibitem{bermond-al}
  J.C. Bermond et al.,
  Hypergraphes hamiltoniens.
  {\em Probl\`{e}mes combinatoires et th\'{e}orie des graphes, Colloq.
  Internat. CNRS, Paris} 260 (1973) 39-43.

\bibitem{bryant}
  D. Bryant et al.,
  Decompositions of complete 3-uniform hypergraphs into small 3-uniform hypergraphs.
  {\em Australas. J. Combin}. 60 (2014), 227-254.

\bibitem{bryant-graph}
  D. Bryant and S. El-Zanati,
  Graph Decompositions,
  in {\em The CRC Handbook of Combinatorial Designs}, 2nd edition
  (Eds. C.J. Colbourn and J.H. Dinitz),
  CRC Press, Boca Raton (2007), 477-486.

%\bibitem{chek-raja}
%  C. Cheruki and A. Rajaraman,
%  Conjunctive query containment revisited.
%  {\em Theoret. Comput. Sci.} 239 (2000), 211-229.
  
%\bibitem{dicre-galdi}
%  G. Di Crescenzo and C. Galdi,
%  Hypergraph Decomposition and Secret Sharing.
%  {\em Discrete App. Math.} 157.5 (2009) 928-946.

\bibitem{feng-chang2}
  T. Feng and Y. Chang,
  Decompositions of the 3-uniform hypergraphs $K_v^{(3)}$ into hypergraphs of a
  certain type.
  {\em Science in China(A)}. 50 (2007), 1035-1044.

\bibitem{feng-chang}
  T. Feng and Y. Chang,
  Decompositions of 3-uniform hypergraph $K_v^{(3)}$ into hypergraph $K_4^{(3)}
  + e$.
  {\em Util. Math.} 87 (2012), 49-64.

%\bibitem{gibb-oste}
%  P.B. Gibbons and P.R. Ostergard.
%  Computational Methods in Design Theory,
%  in {\em The CRC Handbook of Combinatorial Designs}, 2nd edition
%  (Eds. C.J. Colbourn and J.H. Dinitz),
%  CRC Press, Boca Raton (2007), 755-783.

%\bibitem{gott2}
%  G. Gottlob, N. Leone and F. Sarcello,
%  Hypertree Decompositions: A Survey.
%  {\em Mathematical Foundations of Computer Science}.
%  Springer Berlin Heidelberg (2001), 37-57.

%\bibitem{gott}
%  G. Gottlob, N. Leone and F. Sarcello,
%  Hypertree Decompositions and Tractable Queries.
%  {\em J. Comput. Syst. Sci.}. 64 (2002), 579-627.

%\bibitem{gott3}
%  G. Gottlob, N. Leone and F. Sarcello,
%  Robbers, marshals, and guards: game theoretic and logical characterizations of hypertree width.
%  {\em J. Comput. Syst. Sci.}. 66 (2003) 755-808.

%\bibitem{gott4}
%  G. Gottlob et al.,
%  Hypertree Decompositions: Structure, Algorithms, and Applications.
%  {\em Graph-theoretic concepts in computer science}.
%  Springer Berlin Heidelberg (2005), 1-15.

\bibitem{hanani}
  H. Hanani,
  On quadruple systems,
  {\em Canad. J. Math.} 12 (1960), 145-157.

\bibitem{kato-kier}
  G.Y. Katona and H.A. Kierstead,
  Hamiltonian chains in hypergraphs,
  {\em J. Graph Theory} 30 (1999), 205-212.

\bibitem{keevash}
  P. Keevash,
  The existence of designs,
  {\tt arXiv:1401.3665} (2014), 56 pages.

\bibitem{khos-laue}
  G.B. Khosrovshahi and R. Laue,
  $t$-Designs with $t \geq 3$,
  in {\em The CRC Handbook of Combinatorial Designs}, 2nd edition
  (Eds. C.J. Colbourn and J.H. Dinitz),
  CRC Press, Boca Raton (2007), 79-101.

\bibitem{kuhl-schr}
  J. Kuhl and M. W. Schroeder,
  Hamilton cycle decompositions of $k$-uniform $k$-partite hypergraphs.
  {\em Australas. J. Combin}. 56 (2013), 23-37.

\bibitem{kuhn-osthus}
  D. K\"{u}hn and D. Osthus,
  Decompositions of complete uniform hypergraphs into Hamilton Berge cycles.
  {\em J. Combin. Theory, Series A} 126 (2014), 128-135.

\bibitem{mesz-rosa}
  M. Meszka and A. Rosa,
  Decomposing complete 3-uniform hypergraphs into Hamiltonian cycles.
  {\em Australas. J. Combin}. 45 (2009), 291-302.

\bibitem{mohascy}
  H. Moh\'{a}csy and D. K. Ray-Chaudhuri,
  A Construction for Infinite Families of Steiner 3-Designs,
  {\em J. Combin. Theory, Series A} 94 (2001), 127-141.

\bibitem{mull-gron}
  R. C. Mullin and H-D. O. K. Gronau,
  PBDs and GDDs: The Basics,
  in {\em The CRC Handbook of Combinatorial Designs}, 2nd edition
  (Eds. C.J. Colbourn and J.H. Dinitz),
  CRC Press, Boca Raton (2007), 231-236.

\bibitem{verall}
  H. Verall,
  Hamilton decompositions of complete 3-uniform hypergraphs,
  {\em Discrete Math.} 132 (1994), 333-348.

\end{thebibliography}
